Inferring Graphics Programs from Images

### 2017-05-14 extrapolations.tex
updated extrapolation results

@@

@@

@@

@@

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-6.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-6-extrapolation.png}
    \end{tabular}

>>>>

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-3.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-3-extrapolation.png}
    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-6.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-6-extrapolation.png}
    \end{tabular}        
            \\

@@

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-18.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-18-extrapolation.png}
    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-20.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-20-extrapolation.png}
    \end{tabular}        
            \\

@@

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-24.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-24-extrapolation.png}
    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-26.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-26-extrapolation.png}
    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-30.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-30-extrapolation.png}
    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-34.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-34-extrapolation.png}
    \end{tabular}        
            \\

@@

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-45.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-45-extrapolation.png}
    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-48.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-48-extrapolation.png}
    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-49.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-49-extrapolation.png}
    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-52.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-52-extrapolation.png}
    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-56.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-56-extrapolation.png}
    \end{tabular}        
            \\

@@

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-70.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-70-extrapolation.png}
    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-74.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-74-extrapolation.png}
    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-75.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-75-extrapolation.png}
    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-77.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-77-extrapolation.png}
    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-83.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-83-extrapolation.png}
    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-85.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-85-extrapolation.png}
    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-86.png}&
    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-86-extrapolation.png}
    \end{tabular}
